Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-12-16 R0V0.tex
Item 2

\mypara Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure. The main underlying concept employed for the synthesis of feedback laws is the Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}. In terms of computation, controller design problems are often translated in terms of dynamic programming.

>>>>

\mypara Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure. One of the main underlying concepts employed for the synthesis of feedback laws is Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}. In terms of computation, controller design problems are often translated in terms of optimization.
